Blocking-resistant communication\\through domain fronting

### 2014-07-29 docs/meek.tex
Miscellaneous revisions.

In this paper we describe ``domain fronting,'' a general-purpose technique
based on HTTPS that hides the true destination of a communication
from a censor.
Fronting works with many web services that host multiple domain names
behind an HTTPS frontend server.
These include such high--collateral damage infrastructure as
big content delivery networks (CDNs)
and Google's panoply of services---a nontrivial fraction of the web.
Domain fronting can be used as a means of tunneling traffic
to a general-purpose proxy,
so it is not limited to HTTPS, nor to the domains of any specific web service.

@@

Domain fronting and HTTPS take care of two big circumvention challenges,
namely hiding the destination and obscuring the contents of the message.
There remain other, more subtle, meta-attributes of communication
that could serve as a basis for blocking.
For example, the handshake is a fingerprintable part of TLS.
Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
in order that meek's TLS and HTTPS characteristics
match those of a browser as closely as possible.
One of our goals for meek is to force the censor
to employ more sophisticated, expensive, and error-prone statistical tests
to classify traffic as allowed or prohibited,
rather than simple domain blacklists or deep packet inspection;
to force the frontier of censorship
to be a frontier not of simple in-line packet filters,
but of probabilities and false positives.
A preliminary analysis of meek's resistance to detection
based on traffic characteristics like packet size and timing
appears in Section~\ref{sec:trafficstatistics}.
The analysis is based on comparing traffic traces of meek
with samples of HTTPS traffic at an Internet router.

@@

HTTP is fundamentally a request-based protocol.
There is no way for the server to ``push'' data to the client without
having first received a request.
In order to enable the server to send back data,
meek uses one of two techniques.
The first is polling:
every so often the client sends a request with an empty payload
if it has nothing else to send.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
% Implemented in Psiphon's version.
The other technique is to use
long-lived persistent HTTP connections.
When the server sends a response, it keeps the connection open,
continually appending data to the response body while it has anything to send.
When the server receives a new request from the same client,
it closes any response it has open to the client and starts a new response.
See Section~\ref{sec:otherdeployment} for more details
on when each technique may be used;
it depends on the intermediate web service.

@@

Domain fronting defeats address-based blocking and active probing.
HTTPS foils the most straightforward DPI,
hiding byte patterns in the underlying stream.
The censor may try to apply more careful DPI in order to
distinguish fronted and non-fronted traffic.
This section is about TLS fingerprinting,
which is the censor's remaining easy distinguisher,
and how we use a web browser with an unremarkable TLS fingerprint
to disguise the HTTPS tunnel.
The next section is about more subtle and hard-to-apply forms of DPI.

@@

\section{Camouflage of traffic characteristics}
\label{sec:trafficstatistics}

@@

To collect the traffic trace of meek, we browses the Alexa top 500 websites sequentially using 
the Tor Browser Bundle and dump the traffic trace from the network interface. We ensured only
the browser can successfully access the network by setting
up the \texttt{iptables} firewall so that packets from other processes will be dropped. We also 
obtain a 10-minute sample of normal HTTPS traffic trace from LBL. The trace is 983 MB in total. 
We also specifically extracted the traffic between LBL and Google from the trace. Since the trace 
only has packet headers, we cannot extract the domain information. However, the \texttt{TXT} DNS
records of the domain \texttt{\_netblocks.google.com} shows the IP address blocks that belongs to
Google. Therefore, we determine whether a flow is from or to Google by examining the address in the 
IP header. We only interested in the Google traffic only, because the censor who wants to defeat meek
will be mostly likely to compare suspicious traffic with normal Google traffic. The size of the 
Google trace is 312 MB.

@@

@@

>>>>

In this paper we describe ``domain fronting,'' a general-purpose technique
based on HTTPS that hides the true destination of a communication
from a censor.
Fronting works with many web services that host multiple domain names
behind an HTTPS frontend server.
These include such high--collateral damage infrastructure as
big content delivery networks (CDNs)
and Google's panoply of services---a nontrivial fraction of the web.
See Section~\ref{sec:survey} for a listing of some suitable services.
Domain fronting can be used as a means of tunneling traffic
to a general-purpose proxy,
so it is not limited to HTTPS, nor to the domains of any specific web service.

@@

Domain fronting and HTTPS take care of two big circumvention challenges,
namely hiding the destination and obscuring the contents of the message.
There remain other, more subtle, meta-attributes of communication
that could serve as a basis for blocking.
For example, the handshake is a fingerprintable part of TLS.
Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
in order that meek's TLS and HTTPS characteristics
match those of a browser as closely as possible.
One of our goals for meek is to force the censor
to employ more sophisticated, expensive, and error-prone statistical tests
to classify traffic as allowed or prohibited,
rather than simple domain blacklists or deep packet inspection;
to force the frontier of censorship
to be a frontier not of simple in-line packet filters,
but of probabilities and false positives.
A preliminary analysis of meek's resistance to detection
based on traffic characteristics like packet size and timing
appears in Section~\ref{sec:analysis}.
The analysis is based on comparing traffic traces of meek
with samples of HTTPS traffic at an Internet router.

@@

HTTP is fundamentally a request-based protocol.
There is no way for the server to ``push'' data to the client without
having first received a request.
In order to enable the server to send back data,
meek uses one of two techniques.
The first is polling:
every so often the client sends a request with an empty payload
if it has nothing else to send.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
% Implemented in Psiphon's version.
The other technique,
implemented in Psiphon's version of meek,
uses long-lived persistent HTTP connections.
When the server sends a response, it keeps the connection open,
continually appending data to the response body while it has anything to send.
When the server receives a new request from the same client,
it closes any response it has open to the client and starts a new response.
This second technique doesn't work on all services:
notably Google App Engine doesn't support streaming downloads of this kind.

@@

Domain fronting defeats address-based blocking and active probing.
HTTPS foils the most straightforward DPI,
hiding byte patterns in the underlying stream.
The censor may try to apply more careful DPI in order to
distinguish fronted and non-fronted traffic.
This section is about TLS fingerprinting,
which is the censor's remaining easy distinguisher,
and how we use a web browser with an unremarkable TLS fingerprint
to disguise the HTTPS tunnel.
Section~\ref{sec:analysis} is about more subtle and hard-to-apply forms of DPI.

@@

\section{Analysis}
\label{sec:analysis}

@@

To collect the traffic trace of meek, we browses the Alexa top 500 websites sequentially using 
the Tor Browser Bundle and dump the traffic trace from the network interface. We ensured only
the browser can successfully access the network by setting
up the \texttt{iptables} firewall so that packets from other processes will be dropped. We also 
obtain a 10-minute sample of normal HTTPS traffic trace from LBL. The trace is 983~megabytes in total. 
We also specifically extracted the traffic between LBL and Google from the trace. Since the trace 
only has packet headers, we cannot extract the domain information. However, the \texttt{TXT} DNS
records of the domain \texttt{\_netblocks.google.com} shows the IP address blocks that belongs to
Google. Therefore, we determine whether a flow is from or to Google by examining the address in the 
IP header. We only interested in the Google traffic only, because the censor who wants to defeat meek
will be mostly likely to compare suspicious traffic with normal Google traffic. The size of the 
Google trace is 312~megabytes.

@@

% Censors that know no bounds: China on Google, Egypt.

@@

% Prevalence of no SNI.
